Precise spiking motifs in neurobiological and neuromorphic data

### 2022-12-19 manuscript.tex
Update on Overleaf.

Indeed, our focus was implicitly on mammals. worse, we were sometimes using evidence form insects without highlighting the differences. We believe that the coding principle we put forward is general enough to cover both orders. We also tried to keep the review at a reasonable length to keep the balance between computational and biological evidence. Therefore, while we keep our focus on mammals, we have been careful now to mention the order of animals.

@@

Indeed, we had made that choice to

>>>>

Indeed, our focus was implicitly on mammals while we were sometimes using evidence from insects without highlighting the differences. We believe that the coding principle we put forward is general enough to cover both orders. We also tried to keep the review at a reasonable length to keep the balance between computational and biological evidence. Therefore, while we keep our focus on mammals, we have been careful now to mention the order of animals.

@@

Indeed, we had made that choice to study precise temporal motifs. In the new manuscript, we mention these alternative options briefly even if we keep the focus on deterministic spiking motifs for this review.
